G\"{o}del's Ontological Proof of God's Existence (Draft)

### 2013-08-18 Natural Deduction/GodProof-ND.tex
Add ToDo reminder
Fix typo

\textbf{Definitions:}
\begin{itemize}
\item \textbf{(D1)} An individual is a \emph{God} if and only if he possesses all positive properties:
$$
G(x) \biimp \forall \varphi. [P(\varphi) \to \varphi(x)]
$$
\item \textbf{(D2)} A property is \emph{essential} for an individual if and only if it holds for that inidividual and necessarily entails every other property that holds for that individual: $\ess{\varphi}{x} \biimp \varphi(x) \wedge \all \psi. (\psi(x) \imp \nec \all x. (\varphi(x) \imp \psi(x)))$
\end{itemize}

@@

@@

\begin{small}
\begin{prooftree}
\AXC{$ $} \dashedLine \RightLabel{\textbf{S5}}
\UIC{$ \all \varphi. [\pos \ldots \pos \nec \varphi \biimp \nec \varphi] $}
\UIC{$ \pos \nec \ex x. G(x) \biimp \nec \ex x. G(x) $}
        \AXC{$ $} \dashedLine \RightLabel{Th. 2}
        \UIC{$\pos \ex x. G(x)$}
                \AXC{$ $} \dashedLine \RightLabel{Th. A}
                \UIC{$\ex z. G(z) \imp \nec \ex x. G(x)$}
            \BIC{$\pos \nec \ex x. G(x)$}
    \BIC{$\nec \ex x. G(x)$}
\end{prooftree}
\end{small}

>>>>

\textbf{Definitions:}
\begin{itemize}
\item \textbf{(D1)} An individual is a \emph{God} if and only if he possesses all positive properties:
$$
G(x) \biimp \forall \varphi. [P(\varphi) \to \varphi(x)]
$$
\item \textbf{(D2)} A property is \emph{essential} for an individual if and only if it holds for that individual and necessarily entails every other property that holds for that individual: $\ess{\varphi}{x} \biimp \varphi(x) \wedge \all \psi. (\psi(x) \imp \nec \all x. (\varphi(x) \imp \psi(x)))$
\end{itemize}

@@

ToDo: This section still needs more details. See Coq formalization for more details.

@@

\begin{small}
\begin{prooftree}
\AXC{$ $} \dashedLine \RightLabel{\textbf{S5}}
\UIC{$ \all \varphi. [\pos \ldots \pos \nec \varphi \biimp \nec \varphi] $}
\UIC{$ \pos \nec \ex x. G(x) \biimp \nec \ex x. G(x) $}
        \AXC{$ $} \dashedLine \RightLabel{Th. 2}
        \UIC{$\pos \ex x. G(x)$}
                \AXC{$ $} \dashedLine \RightLabel{Th. A}
                \UIC{$\ex z. G(z) \imp \nec \ex x. G(x)$} \doubleLine
            \BIC{$\pos \nec \ex x. G(x)$}
    \BIC{$\nec \ex x. G(x)$}
\end{prooftree}
\end{small}
